Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-03 causal-bandit/icml-2015/experiments.tex
puts latest figures into experiments

>>>>

\begin{figure}
\caption{Simple regret vs number of variables, $N$, for $T=250$, for Successive Rejects and, Causal-Best-Arm-Identification on the confounded bandit problem. Error bars show standard error from 10000 simulations.}
\label{fig:simple_vs_N_confounded}
\centering
\includegraphics[width=.5\textwidth]{exp_general_simpleregret_vs_N_T250_sims10000_20160131_080208.pdf}
\end{figure}

\subsection{Experiments on more general graphs}
We now demonstrate the general simple regret algorithm on some graphs that display some interesting behaviour.

\begin{figure}[h]
\centering
\caption{Causal model for the confounded bandits problem.}
\label{fig:causalStructure_confounded_N}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed}, hidden/.style={empty}]
\node[main node](1){$X_{2}$};
\node[main node, right=of 1](2){$X_{3}$};
\node[hidden, right=of 2](3){$...$};
\node[main node, right=of 3](4){$X_{N}$};
\node[main node, below right=of 2](5){Y};
\node[main node,above right=of 2](6){$X_1$}; 
 \path[every node/.style={font=\sffamily\small}]
    (1) edge (5)
    	(2) edge (5)
    (4) edge (5)
    (6) edge (1) edge (2) edge (4);
\end{tikzpicture}
\end{figure}

\subsubsection{X1-dominated confounded model}
A model under which the value of the confounding variable $X_1$ plays the central role in determining $P(Y)$.  Let:
\eq {
\P{Z = 1} &= q \\
\P{X_k = 1|Z=j} &=  q_j \;\; \forall k \in \set{1...n}\\
\P{Y|x_1 ... x_n} &= \bar{\boldsymbol{x}}
} 
This leads to rewards:
\eq {
\P{Y|do(Z = j)} = q^j(1-q)^{1-j}\\
\P{Y|do(X_i = j)} = \begin{cases}
\frac{1}{n} + \frac{n-1}{n}\left(q q_1 + (1-q)q_0 \right) & \text{ if } j = 1 \\
\frac{n-1}{n}\left(q q_1 + (1-q)q_0 \right) & \text { if } j = 0
\end{cases}
}

We can select the probabilities to create a scenario close to the worst case problem such that there is a single arm $do(Z=1)$ that is optimal with expected reward ...
